---
title: "Advanced Financial Data Analytics Quiz"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)
tutorial_options(exercise.checker = gradethis::grade_learnr)
```

## Introduction

This interactive tutorial tests your understanding of reproducible financial analytics, the importance of R packages, and the role of APIs and databases in finance.

To run this tutorial:

1.  Save the content in an `.Rmd` file.
2.  Open the file with RStudio.
3.  Click on "Run Document" to start the tutorial in a Shiny app.

This interactive tutorial will guide the learner through multiple-choice questions, providing immediate feedback on their answers. It's a great way to reinforce learning and assess understanding of the course material.

### Question 1: Reproducible Analytics

What does it mean for financial analytics to be "reproducible"?

```{r question-1, echo=FALSE}
quiz(
  question = "What does it mean for financial analytics to be 'reproducible'?",
  answer("The results can only be achieved once and cannot be duplicated."),
    answer("The analysis can be repeated by others, using the same data and code to achieve the same results.",correct = TRUE),
    answer("The analysis is conducted without the use of scripts or version control."),
    answer("Only the original author can reproduce the analysis."),
  "The analysis can be repeated by others, using the same data and code to achieve the same results.",
  incorrect = c(
    "Incorrect. Reproducible analytics means the results can be duplicated by others using the same resources.",
    "Correct! Reproducible analytics ensures that anyone can replicate the results using the same data and code.",
    "Incorrect. The use of scripts and version control is often crucial for reproducibility.",
    "Incorrect. The goal of reproducibility is to allow anyone, not just the original author, to reproduce the results."
  )
)
```

### Question 2: Toolkits for Reproducibility

Which of the following tools is NOT directly associated with reproducible financial analytics?

```{r question-2, echo=FALSE}
quiz(
  question = "Which of the following tools is NOT directly associated with reproducible financial analytics?",
  answer("R"),
    answer("Quarto"),
    answer("Git / GitHub"),
    answer("PowerPoint",correct = TRUE),
  incorrect = c(
    "Incorrect. R is a fundamental tool for statistical computing and analytics.",
    "Incorrect. Quarto is used for literate programming, integrating code, narrative, and output.",
    "Incorrect. Git / GitHub is essential for version control and sharing code.",
    "Correct! PowerPoint is not directly associated with reproducible analytics; it's more of a presentation tool."
  )
)
```

### Question 3: R Packages and CRAN

As of September 2020, approximately how many R packages were available on CRAN?

```{r question-3, echo=FALSE}
quiz(
  question = "As of September 2020, approximately how many R packages were available on CRAN?",
 answer("Over 1,600"),
    answer("Over 16,000",correct = TRUE),
    answer("Over 160,000"),
    answer("Over 6,000"),
  incorrect = c(
    "Incorrect. There were significantly more than 1,600 packages.",
    "Correct! As of September 2020, there were over 16,000 R packages available on CRAN.",
    "Incorrect. The number is large, but not quite that large.",
    "Incorrect. There were more than 6,000 packages, indicating the extensive availability of tools for R users."
  )
)
```

### Question 4: Essentials of R Coding

In R, how can you access documentation for a specific function, such as `mean`?

```{r question-4, echo=FALSE}
quiz(
  question = "In R, how can you access documentation for a specific function, such as `mean`?",
  answer("mean?"),
    answer("?mean",correct = TRUE),
    answer("help(mean)"),
    answer("All of the above"),
  incorrect = c(
    "Incorrect. The correct syntax uses a question mark before the function name.",
    "Correct! Prepending a question mark to the function name is the standard way to access its documentation.",
    "Incorrect. While `help(mean)` is a valid command, the syntax provided in the options is incorrect for this context.",
    "Incorrect. Only the second option is the conventional method to access documentation for a specific function in R.")
)
```

### Question 5: APIs and Databases in Finance

Why are APIs and databases considered crucial in financial data analytics? Select all that apply:

```{r question-5, echo=FALSE}
quiz(
 

 question = "Why are APIs and databases considered crucial in financial data analytics? Select all that apply:",
  answer("They allow for real-time data access.",correct = TRUE),
    answer("They enable automatic updating of financial models."),
    answer("They provide structured data management for large volumes of data.",correct=TRUE),
    answer("They can only be used by experienced data scientists."
  ),
incorrect = c(
    "Correct. Real-time data access is crucial for timely financial analysis.",
    "This statement is misleading. While APIs and databases facilitate data access and management, they don't automatically update financial models; the models need to be designed to incorporate new data.",
    "Correct. Structured data management is essential for handling and analyzing large volumes of financial data efficiently.",
    "Incorrect. APIs and databases are tools that can be learned and used by individuals at various skill levels, not just experienced data scientists."
  )
)
```

## Conclusion

You've completed the quiz! These questions are designed to test your understanding of key concepts in financial data analytics and the importance of reproducibility, R packages, and the use of APIs and databases. Continue exploring these tools and techniques to enhance your skills in financial data science.
